%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{marvosym}
\usepackage{amsmath}
\usepackage{eso-pic}% http://ctan.org/pkg/eso-pic
\usepackage{lipsum}% http://ctan.org/pkg/lipsum
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{color}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}

\rfoot{Page \thepage\ of \pageref{LastPage}}

\newcommand{\sectionspace}{\vspace{3mm}}
\newcommand{\simplelistentry}[3]{\textit{#1}, {#2} \hfill {#3}}
\newcommand{\fixme}{\textcolor{red}{\textbf{fix me}} \space}
\newcommand{\attention}[1]{\noindent \fixme \textcolor{red}{#1}}

\name{Jos\'{e} J. Fuentes Aguayo} % Your name

\address{\Telefon \space Cell: (787) 457 - 1565}
\address{e\Letter \space jjfuentes7@gmail.com}
\address{\Letter \space 501 Camino Los Pizarro Alturas de San Juan 622
  \textbullet San Juan, PR 00926}


\begin{document}

%% % add 'US Citizen' at top right corner of first page
%% \AddToShipoutPictureBG*{%
%%   \AtPageUpperLeft{%
%%     \hspace{\paperwidth}%
%%     \raisebox{-\baselineskip}{%
%%       \makebox[-25pt][r]{US Citizen}
%% }}}%



%------------------------------------------------------------------------------
%	SUMMARY SECTION
%------------------------------------------------------------------------------

\begin{rSection}{Summary}

\begin{itemize}
\item Project Manager with demonstrated scheduling, cost control, risk
  management, leadership, business case writing and delivery in contract
  management, accounting, procurement, and business process improvement
  activities.
\item Liaison between IT and administrative departments of the Federal, Private,
  and Non-Profit Sector focusing and implementing innovative and practical
  business solutions for complex business challenges while managing
  stakeholders’ expectations. \\
\end{itemize}

\end{rSection}



%------------------------------------------------------------------------------
%	EDUCATION SECTION
%------------------------------------------------------------------------------

%% \sectionspace
\begin{rSection}{Education}

{\bf Universidad Ana G. Mendez} \hfill {\bf San Juan, PR} \\
\textit{MBA in Information Systems Technology} \hfill Expected graduation date:
June 2021 \\

{\bf University of Puerto Rico at Humacao (UPRH)} \hfill {\bf Humacao, PR} \\
\textit{Bachelors Of Business Administration} \hfill May 2012 \\

{\bf PMP Certification Course} \hfill {\bf San Juan, PR} \\
\textit{PMI Project Management Professional Member License - 4499504} \hfill
June 2016 \\

\end{rSection}



%------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%------------------------------------------------------------------------------

%% \sectionspace
\begin{rSection}{Work Experience}
%------------------------------------------------

\begin{rSubsection}{eliteBco LLC - Elite
    Business Consultants $\vert$ San Juan, PR}{June 2012 - present}{Project
    Manager}{\space}

\item
\begin{itemize}
\item Manage Agiloft's Contract Lifecycle Management (CLM) solutions.

\item Generate product and process system documentation for all software
  projects.

\item Generate project documents such as project schedule, risk management,
  issues logs, project budget, communication plan, project status report,
  project charter, meeting agenda and minutes, quality assurance (QA) test
  plan, and project management plan.

\item Manage numerous technical projects for US, Canada, and Latin America
  locations for corporations in Biomedical, Healthcare, Research Institute,
  Government, and Education industries.

\item Participate in the design, planning, and implementation of a \$13 million
  software solution for payment and reimbursement portal service infrastructure
  worldwide. Currently provide ongoing support and monitoring cloud services to
  support large volume of users.

\item Provide administrative support for software applications and IT.

\item Manage project definitions to include validated functional requirements,
  scope, roles, responsibilities, budgets, timescales, and resources.

\item Lead the overall technical vision for a particular solution.

\item Serve as main point of contact for all communications between customer,
  management, and company in addition to managing resources to ensure milestones
  are achieved within agreed timeframes.

\end{itemize}

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{\space}{\space}{Senior Consultant}{\space}

\item
\begin{itemize}
\item Identify, analyze, measure, and manage project risks, track records of
  expenditure, accounting, costing and billing, and conduct impact analysis to
  assess consequences of project deliverables.

\item Collaborate with C-level department managers and directors to exchange
  information, present new approaches, discuss project status, and identify
  opportunities.

\item Provide training for more than a 100+ audience as well as management and
  end user profiles.

\item Business developer including proposal writing and project procurement.

\item Implement accounting and procurement software solutions for the federal
  and non-for-profit sector with the design of workflows as well as management
  of stakeholder expectations.

\item Manage the IT department to support 28 locations of Starbucks in PR
  throughout the merger with EFI (Empresas Fonalledas). Participated in decision
  making for new IT infrastructure.

\end{itemize}

\end{rSubsection}


%------------------------------------------------

\sectionspace
\begin{rSubsection}{POPULAR INC. $\vert$ East Region Branches, PR}{October 2007
    - June 2012}{Bank Representative}{\space}

\item
\begin{itemize}
\item Processed deposits, withdrawals, check cashing, and other bank
  transactions, including night deposits and ATM.

\item Processed sensitive data credentials in electronic bank structure systems,
  including contact information and, commercial cash deposits account.

\item Identified opportunities to cross-sell bank products and services, and
  provided referrals to appropriate account managers.

\item Provided new staff training on operational processes and compliance.

\end{itemize}

\end{rSubsection}


%------------------------------------------------
\end{rSection}



%------------------------------------------------------------------------------
%	SKILLS SECTION
%------------------------------------------------------------------------------

\sectionspace
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
  Databases & Windows Server 2008-2016, Oracle DB, SQL, MS Access \\

  Operating Systems & Most Windows OS, Apple OS \\

  General Software & MS Office 365 applications, Visio, Project, VMware, Sage
  300 ERP \\

  Technical Skills & IMB Cloud, Salesforce Integration, Symphony Enterprise
  Management \\

  Agiloft Modules & Contract Management, CRM, BPM, ITIL \\

  Abila Modules & MIP Fund Accounting, Fundraising CRM \\

  Microix Workflow Modules & Requisitions, Inventory, Budget, Timesheet \\

  Infrastructure Systems & Active Directory, Domain Controllers, networking,
  email admin services \\

  Hardware & Cisco routers, server setup, Ricoh and Xerox, Oracle/Micros Res
  3700 \\

  General Skills & Business Analysis, Software Integration, Agile Methodologies \\

  \space & Software Development Life Cycle (SDLC), IT
  Service Management, \\

  \space & Business Process Design, Pre-Sales activities, Gathering \\

  \space & Customer Requirements, Following and Measuring Development Process \\

  Languages & Fully proficient in English and Spanish.

\end{tabular}

\end{rSection}




%------------------------------------------------------------------------------
%	REFERENCES SECTION
%------------------------------------------------------------------------------

\sectionspace
\sectionspace
\begin{rSection}{References}
Available upon request.
\end{rSection}


%------------------------------------------------------------------------------

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
